Cross-lingual Document Similarity and Event Detection \todo{Better title...}

### 2015-03-10 rupnik2015.tex
- added evaluation using different models

>>>>

\begin{table}[h]
\caption{Accuracy of story linking with features obtained from different cross-lingual similarity models}
\label{table:linkingEvalModels}
\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  \cline{1-4}
  Models & CA & Precision & Recall \\ \cline{1-4}
  CCA & 77.6\% & 0.783 & 0.811 \\ \cline{1-4}
  $k$-means & 73.9\% & 0.695 & 0.846 \\ \cline{1-4}
  LSI & 76.1\% & 0.755 & 0.769 \\ \cline{1-4}
  \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[h]
\caption{Accuracy of story linking with different sets of features}
\label{table:linkingEval}
\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  \cline{1-4}
  Features & CA & Precision & Recall \\ \cline{1-4}
  CCA & 77.6\% & 0.783 & 0.811 \\ \cline{1-4}
  Concepts & 88.8\% & 0.884 & 0.891 \\ \cline{1-4}
  Misc & 65.3\% & 0.718 & 0.500 \\ \cline{1-4}
  CCA + concepts & 89.2\% & 0.891 & 0.893 \\ \cline{1-4}
  All & 89.6\% & 0.895 & 0.895 \\ \cline{1-4}
  \hline
\end{tabular}
\end{center}
\end{table}
